%\documentclass[conference]{./template/IEEEtran}
\documentclass[conference]{acm_proc_article-sp}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{myart,times}
% \usepackage{stfloats}
\usepackage{listings}
\usepackage{fancyvrb}
% \usepackage{framed}
% \usepackage{caption}
\usepackage{subcaption}
% \usepackage{subfigure}
%\usepackage{amsthm}
\usepackage[]{algorithm2e}
\usepackage[disable]{todonotes}
\presetkeys{todonotes}{inline}{}
\newcommand{\done}[2]{\todo[color=green!40]{#1\bf{#2}}}


% \usepackage[listings,skins]{tcolorbox}
\hyphenation{op-tical net-works semi-conduc-tor}
\newtheorem{definition}{Definition}
\newcommand{\titlea}{Static Detection and Automatic Exploitation of Intent Message Vulnerabilities in Android Applications}
\newcommand{\titleb}{Analysis of Android Applications for Intent Message Vulnerabilities}
\newcommand{\titlec}{Android Message Passing Analysis}
\newcommand{\titled}{Practical Exploit Generation for Intent Message Vulnerabilities in Android}
\begin{document}
\title{\titled}


% \author{
% \IEEEauthorblockN{Daniele Gallingani}
% \IEEEauthorblockA{University of Illinois at Chicago\\
% Chicago, IL\\
% Politecnico di Milano\\
% Milano, Italy\\
% Email: dgalli3@uic.edu}
% \and
% \IEEEauthorblockN{Rigel Gjomemo, V.N. Venkatakrishnan}
% \IEEEauthorblockA{University of Illinois at Chicago\\
% Chicago, IL\\
% Email: \{rgjome1,venkat\}@uic.edu}
% \and
% \IEEEauthorblockN{Stefano Zanero}
% \IEEEauthorblockA{Politecnico di Milano\\
% Milano, Italy\\
% Email: stefano.zanero@polimi.it}
% }

%\numberofauthors{4}
%\author{
%\alignauthor
%Daniele Gallingani\\
%       \affaddr{University of Illinois at Chicago}\\
%       \affaddr{Chicago, IL}\\
%       \affaddr{Politecnico di Milano}\\
%       \affaddr{Milano, Italy}\\
%       \email{dgalli3@uic.edu}\\
%       \email{daniele.gallingani@mail.polimi.it}
%\alignauthor
%Rigel Gjomemo\\
%       \affaddr{University of Illinois at Chicago}\\
%       \affaddr{Chicago, IL}\\
%       \email{rgjome1@uic.edu}
%\alignauthor
%V.N. Venkatakrishnan\\
%       \affaddr{University of Illinois at Chicago}\\
%       \affaddr{Chicago, IL}\\
%       \email{venkat@uic.edu}
%\alignauthor
%\and
%Stefano Zanero\\
%       \affaddr{Politecnico di Milano}\\
%       \affaddr{Milano, Italy}\\
%       \email{stefano.zanero@polimi.it}
%}

% \author{
% \IEEEauthorblockN{
% Daniele Gallingani\IEEEauthorrefmark{1},
% Rigel Gjomemo\IEEEauthorrefmark{2},
% V.N. Venkatakrishnan\IEEEauthorrefmark{3} and
% Stefano Zanero\IEEEauthorrefmark{4}
% }
% \IEEEauthorblockA{\IEEEauthorrefmark{1}University of Illinois at Chicago\\
% Chicago, IL\\
% Politecnico di Milano\\
% Milano, Italy\\
% Email: dgalli3@uic.edu}
% \IEEEauthorblockA{\IEEEauthorrefmark{2}University of Illinois at Chicago\\
% Chicago, IL\\
% Email: rgjome1@uic.edu}
% \IEEEauthorblockA{\IEEEauthorrefmark{3}University of Illinois at Chicago\\
% Chicago, IL\\
% Email: venkat@uic.edu}
% \IEEEauthorblockA{\IEEEauthorrefmark{4}Politecnico di Milano\\
% Milano, Italy\\
% Email: stefano.zanero@polimi.it}
% }

\maketitle


\begin{abstract}
Android's Inter-Component Communication (ICC) mechanism strongly relies
on  Intent messages. Unfortunately, due to the lack of message
origin verification in Intents, implementing security policies based
on message sources is hard in practice, and completely relies on the
programmer's skill and attention. In this paper, we first review a set of
vulnerabilities that common programming errors might introduce. Second,
we present how these vulnerabilities can be effectively detected automatically
through static analysis. We are thus able to highlight component fragments
that expose vulnerable resources to possible malicious message senders. Most importantly,
we advance the state of the art by developing a method to automatically demonstrate
whether the identified vulnerabilities can be exploited or not, adopting a formal
approach to automatically produce malicious payloads that can trigger
dangerous behavior in vulnerable applications. We therefore eliminate the high rate of false
positives common in previously applied methods.
We test our methods on a representative sample of applications, and we find that 29 out of 
64 tested applications are detected as potentially vulnerable, while
26 out of 29 can be automatically proven to be exploitable. Our experiments demonstrate the
lack of exhaustive sanity checks when receiving messages from unknown sources, and 
stress the underestimation of this problem in real world application development. The techniques
we develop can be used to detect these issues in a completely automated fashion and with much
higher precision than the state-of-the-art.
\end{abstract}


%\IEEEpeerreviewmaketitle

\input{sections/introduction}

\input{sections/problem_statement}

\input{sections/approach}

%\input{sections/analysis}

\input{sections/implementation}

\input{sections/results}

\input{sections/related_work}

\input{sections/conclusions}

\bibliographystyle{template/IEEEtran}
\bibliography{bibliography}

\end{document}
