%\documentclass[conference]{./template/IEEEtran}
%\documentclass[conference]{acm_proc_article-sp}
% \documentclass{sig-alternate}
\documentclass{sig-alternate-2013}

\newfont{\mycrnotice}{ptmr8t at 7pt}
\newfont{\myconfname}{ptmri8t at 7pt}
\let\crnotice\mycrnotice%
\let\confname\myconfname%

\permission{Permission to make digital or hard copies of part or all of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage, and that copies bear this notice and the full citation on the first page. Copyrights for third-party components of this work must be honored. For all other uses, contact the owner/author(s). Copyright is held by the author/owner(s).}
\conferenceinfo{CODASPY'15,}{March 2--4, 2015, San Antonio, Texas, USA.} 
\copyrightetc{ACM \the\acmcopyr}
\crdata{978-1-4503-3191-3/15/03. \\ 
http://dx.doi.org/10.1145/2699026.2699132}

\clubpenalty=10000 
\widowpenalty = 10000




\usepackage{cite}
\usepackage{graphicx}
\usepackage{myart,times}
% \usepackage{stfloats}
\usepackage{listings}
\usepackage{fancyvrb}
% \usepackage{framed}
% \usepackage{caption}
\usepackage{subcaption}
% \usepackage{subfigure}
%\usepackage{amsthm}
\usepackage[]{algorithm2e}
%\usepackage[disable]{todonotes}
%\presetkeys{todonotes}{inline}{}
%\newcommand{\done}[2]{\todo[color=green!40]{#1\bf{#2}}}


% \usepackage[listings,skins]{tcolorbox}
\hyphenation{op-tical net-works semi-conduc-tor}
\newtheorem{definition}{Definition}
\newcommand{\titlea}{Static Detection and Automatic Exploitation of Intent Message Vulnerabilities in Android Applications}
\newcommand{\titleb}{Analysis of Android Applications for Intent Message Vulnerabilities}
\newcommand{\titlec}{Android Message Passing Analysis}
\newcommand{\titled}{Practical Exploit Generation for Intent Message Vulnerabilities in Android}



% \author{
% \IEEEauthorblockN{Daniele Gallingani}
% \IEEEauthorblockA{University of Illinois at Chicago\\
% Chicago, IL\\
% Politecnico di Milano\\
% Milano, Italy\\
% Email: dgalli3@uic.edu}
% \and
% \IEEEauthorblockN{Rigel Gjomemo, V.N. Venkatakrishnan}
% \IEEEauthorblockA{University of Illinois at Chicago\\
% Chicago, IL\\
% Email: \{rgjome1,venkat\}@uic.edu}
% \and
% \IEEEauthorblockN{Stefano Zanero}
% \IEEEauthorblockA{Politecnico di Milano\\
% Milano, Italy\\
% Email: stefano.zanero@polimi.it}
% }

\numberofauthors{4}
\author{
\alignauthor
Daniele Gallingani\\
      \affaddr{University of Illinois at Chicago}\\
      \affaddr{Chicago, IL}\\
      \affaddr{Politecnico di Milano}\\
      \affaddr{Milano, Italy}\\
      \email{daniele.gallingani@mail.polimi.it}
\alignauthor
Rigel Gjomemo\\
      \affaddr{University of Illinois at Chicago}\\
      \affaddr{Chicago, IL}\\
      \email{rgjome1@uic.edu}
\alignauthor
V.N. Venkatakrishnan\\
      \affaddr{University of Illinois at Chicago}\\
      \affaddr{Chicago, IL}\\
      \email{venkat@uic.edu}
\alignauthor
\and
Stefano Zanero\\
      \affaddr{Politecnico di Milano}\\
      \affaddr{Milano, Italy}\\
      \email{stefano.zanero@polimi.it}
}

% \newfont{\mycrnotice}{ptmr8t at 7pt}
% \newfont{\myconfname}{ptmri8t at 7pt}
% \let\crnotice\mycrnotice%
% \let\confname\myconfname%

% \permission{Permission to make digital or hard copies of part or all of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage, and that copies bear this notice and the full citation on the first page. Copyrights for third-party components of this work must be honored. For all other uses, contact the owner/author(s). Copyright is held by the author/owner(s).}
% \conferenceinfo{CODASPY'15,}{March 2--4, 2015, San Antonio, Texas, USA.} 
% \copyrightetc{ACM \the\acmcopyr}
% \crdata{978-1-4503-3191-3/15/03. \\
% http://dx.doi.org/10.1145/2699026.2699132}

% \clubpenalty=10000 
% \widowpenalty = 10000



\begin{document}
\title{\titled}
\conferenceinfo{CODASPY 2015}{Mar 02-04 2015, San Antonio, TX, USA}
\crdata{978-1-23456-78-9/01/23}
\CopyrightYear{2015}
\maketitle
\let\thefootnote\relax\footnote{\it This work was partially supported by National Science Foundation
grants CNS-1065537, CNS-1069311, CNS-12416854}

\begin{abstract}
Android's Inter-Component Communication (ICC) mechanism strongly relies
on  Intent messages. Unfortunately, due to the lack of message
origin verification in Intents, application security completely relies on the
programmer's skill and attention. In this paper, we advance the state of the art 
by developing a method to automatically detect potential vulnerabilities and, most importantly, demonstrate
whether they can be exploited or not. To this end, we adopt a formal
approach to automatically produce malicious payloads that can trigger
dangerous behavior in vulnerable applications. We test our methods on a representative sample of applications, and we find that 29 out of 
64 tested applications are potentially vulnerable, while 
26 of them are automatically proven to be exploitable. 
\end{abstract}

\vspace{1mm}
\noindent
{\bf Categories and Subject Descriptors:} D.4.6 {[Operating Systems]}: {Security and Protection}

\vspace{1mm}
\noindent
{\bf Keywords:} Android, Application Security

\input{sections/introduction}

\input{sections/problem_statement}

\input{sections/approach}

%\input{sections/analysis}

% \input{sections/implementation}

 \input{sections/results}

% \input{sections/related_work}

\input{sections/conclusions}

\bibliographystyle{template/IEEEtran}
\bibliography{bibliography}

\end{document}
